REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case

### 2017-11-21 main.tex
HI -> \ion{H}{1} etc. everywhere. Other small changes

\subsubsection{Ionizing Radiation}
\label{sec:ionizing radiation}
Radiation feedback (ionization, ionization heating, and radiation pressure) is an important source of pre-SN feedback in galaxies. HII regions carved out by stellar radiation change the ISM structure where SNe eventually explode, generally increasing their dynamical importance. However, when accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily through channels carved through dense clouds. Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with limited application in full radiation hydrodynamics simulations \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing. As we seek a complete accounting of stellar feedback physics, we follow \ion{H}{1} and \ion{He}{1} ionizing radiation from our stars through ray tracing methods described below. 
%mm In this particular work, we 
  We here
use two different simulations of the same galaxy to demonstrate the importance of following radiation feedback with full radiative transfer methods (see Section~\ref{sec:IC}).

@@

We also include the effects of radiation pressure on \ion{H}{1}. This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}. We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared. This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}. However, the importance of multiple scattering is still unclear. Other works have shown the effect to only increase the radiation pressure by a factor on order of unity \citep{Krumholz2012,Krumholz2013,Reissl2017}. Due to these uncertainties, and given that we focus on low metallicity dwarf galaxies with low dust content, we ignore this effect.

\subsubsection{Diffusive Heating}
\label{sec:diffusive heating}
We include two forms of diffusive heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \citet{HM2012}, and 2) localized photoelectric (PE) heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars. Photoelectric heating can be a dominant heating mechanism in the ISM \citep{Parravano2003} of the Milky Way, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}. However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contended \citep{Hu2016,Hu2017}. Generally, models for PE heating and LW radiation in hydrodynamic simulations of galaxies adopted a constant value or a static, radial profile. Only recently has the localization and time variation of these processes been considered.

Self-shielding of gas against the metagalactic UV background is important in high resolution simulations, particularly for low-mass, low metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background (see \citep{GrackleMethod} for more details of this implementation). We assume HeI ionization generally follows HI. This allows us to approximate HeI self-shielding using the same form (A. Rahmati, private communication). We ignore HeII photoionization from the UV background entirely. Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from Cloudy (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \texttt{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

@@

Following the initialization procedure of \citet{Hu2017}, we use artificial supernova driving to generate realistic densities and turbulent properties in the galaxy ISM. This additionally prevents an otherwise uniform collapse of the gas disk. The supernovae explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}. We stop the artificial driving 25~Myr after the first star particle forms. These artificial supernova do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.

@@

We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. Each figure gives density weighted projections of number density (first row), temperature slices (second row), HI column density projections (third row), and O column density projections (fourth row), at four different times in the simulation \textit{(list times here)}. In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points. Towards the end of the simulation time, the half light radius is $389 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.

@@

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{textbf{Draft figure - need to pretty up and finalize fields and times.} Edge-on views of our dwarf galaxy at four different times in its evolution, beginning with the time at first star formation and ending at XXX Myr. Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving HI column density (third row) and O column density (fourth row). Additionally, each individual main sequence star particle is shown in the number density projections as a single black dot.}
\label{fig:panel_x}
\end{figure*}

@@

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about \textbf{$6 \times 10^5$ M$_{\odot}$, or roughly 17\%} of the total mass in the galaxy's disk. The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases to about \textbf{25\%} as the total amount of mass in the disk decreases through feedback driven winds. Small drops in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy is discussed further in context with other works in Section~\ref{sec:observation}.

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{sfr_snr}
\includegraphics[width=0.475\linewidth]{mass_evolution}
\caption{Left: The SFR and core collapse SNR in our dwarf galaxy in 10 Myr bins (left). Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the galaxy over time. Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and SNR.}
\label{fig:sfr_mass_evolution}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{1D radial profiles of the ISRF in our galaxy in three different bands, time-averaged over the final 50 Myr of simulation time. The top panel gives $G_{\rm o}$, or the flux of radiation between 6 - 13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position. The bottom panel gives the HI and HeI ionizing stellar radiation flux, showing average value and maximum values only. For these fields the minimum value reaches zero at some point over the examined period at all radii.}
\label{fig:ISRF}
\end{figure}

The bottom panel gives the ionizing photon fluxes (HI and HeI) from ionizing photons from the stellar radiation \texttt{only}. Since these fields are tracked directly with ray-tracing radiative transfer, the profiles encode information about local attenuation of these photons from dense, neutral gas. This is the main driver of the differences between these fields and $G_{\rm o}$. In addition, we only show the average line and shade to the maximum value at any given position, since the minimum value reaches zero at all radii at some point over the 50 Myr examined. As shown, this causes the profile to vary much more dramatically at all radii. However, the same general trend is preserved of less radiation in the inner 200 pc than the region between 200 and 400 pc, and an order of magnitude or more fluctuation at all radii. The rapid drop off beyond 400 pc is due to the rapid attenuation of ionizing photons by the cold gas at large radii (see Figure~\ref{fig:panel_x}).

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within 25 pc of the midplane of our dwarf galaxy. We note the large difference in color scale between the two plots. Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ since we assume it to be optically thin, though do apply a localized shielding approximation.}
\label{fig:ISRF_2D}
\end{figure*}

@@

The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted HI surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, Tollerud2015, Sand2015}. However, the sample of isolated dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small. In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) law (left) for low mass galaxies, and the extended Schmidt law (ESL) (right) which has been shown recently to be extend to low mass, low metallicity dwarf galaxies \citep{Roychowdhury2017}. We plot our galaxy every 1 Myr in these diagrams, showing the significant temporal variation in both spaces. Although these quantities are conceptually simple, due to how these values are measured observationally it is challenging to make a direct comparison to simulations, particularly in defining the geometric region to measure the surface densities. We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs following what is described in \citet{Roychowdhury2014}. We define $\Sigma_{\rm sfr} = \dot{M}_{*, \rm{10 Myr}} / A_{*, \rm{10 Myr}}$, where $\dot{M}_{*, \rm{10 Myr}}$ is the SFR measured over the preceding 10 Myr, and $A_{*, \rm{10 Myr}}$ is the disk defined out to the farthest star formed within the previous 10 Myr. Likewise, $\Sigma_{\rm gas} = M_{\rm gas, 10 Myr} / A_{*, \rm{10 Myr}}$, where M$_{\rm gas, 10 Myr}$ is the total gas mass within this defined disk. However, the total gas content cannot be determined observationally, particularly for low mass dwarf galaxies with a virtually unmeasurable H$_2$ content. Therefore, we present $\Sigma_{\rm gas}$ as measured directly in the simulations (green/purple points) and the observational equivalent, or $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He, and where there is no correction for H$_2$ (plasma points).

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution}
\includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution}
\caption{The KS law (left) and ESL (right) relationships for our galaxy as measured every 1 Myr for the total gas surface density computed from the simulations, and an observational analog derived using the HI content (see text for details).}
\label{fig:KS}
\end{figure*}

@@

Unfortunately, these high resolution simulations are not (yet) run for the $\sim$ Gyr timescales required to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at z = 0. However, we can compare to a key observable, the ejection / retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from stellar evolution models based on the galaxy's star formation history. This can be done readily with Milky Way dSph's, whose stars seem to retain very little of the expected metals produced, on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}. However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy. Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gaseous, star forming low mass dwarf galaxy close enough to the Milky Way to conduct this experiment and with an observable HII region, necessary for determining gas phase abundances. Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}. As discussed in Section~\ref{sec:chemical evolution}, roughly \textbf{95\%} of the tracked metals produced throughout the simulation time no longer reside within the galaxy's disk. At the end of our simulation, we agree with the observations; however, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs. Although more than half of these metals are expected to be re-accreted \citep{Angles-Alcazar2017}, it is still possible that, at any moment, most of the metals that have been produced lie outside the galaxy disk. We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.

@@

\section{Stellar Radiation Properties}
\label{appendix:radiation}
We detail the radiation properties of our model stars as a function of stellar mass and metallicity, both of which are assigned directly from an IMF and from the local gas properties respectively. The stellar radiation properties are a determined from the OSTAR2002 grid \citep{Lanz2003} (or as integrated from an adjusted black body curve for stars off of the OSTAR2002 grid) given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set. In Figure~\ref{fig:stellar radiation properties} we plot the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and LW (middle right) luminosities, and finally the HI ionizing radiation photon energy (bottom left) and HeI ionizing photon energy (bottom right). We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass. This requires two factors for each radiation type, one for low mass and one for high mass stars. We use the following multiplicative factors to adjust the black body spectrum for HI and HeI radiation respectively: [0.1, 3.2] and [0.0001, 4.0]. We do not find this adjustment to be necessary for the FUV and LW radiation bands.

>>>>

\subsubsection{Ionizing Radiation}
\label{sec:ionizing radiation}
Radiation feedback (ionization, ionization heating, and radiation pressure) is an important source of pre-SN feedback in galaxies. \ion{H}{2} regions carved out by stellar radiation change the ISM structure where SNe eventually explode, generally increasing their dynamical importance. However, when accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily through channels carved through dense clouds. Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with limited application in full radiation hydrodynamics simulations \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing. As we seek a complete accounting of stellar feedback physics, we follow \ion{H}{1} and \ion{He}{1} ionizing radiation from our stars through ray tracing methods described below. 
%mm In this particular work, we 
  We here
use two different simulations of the same galaxy to demonstrate the importance of following radiation feedback with full radiative transfer methods (see Section~\ref{sec:IC}).

@@

We also include the effects of radiation pressure on \ion{H}{1}. This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}. We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared. This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}. However, the importance of multiple scattering is still unclear. Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013,Reissl2017}. Due to these uncertainties, and given that we focus on low-metallicity dwarf galaxies with low dust content, we ignore this effect.

\subsubsection{Diffusive Heating}
\label{sec:diffusive heating}
We include two forms of diffusive heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars. Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}. However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}. Generally, models for photoelectric heating and LW radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile. Only recently has the localization and time variation of these processes been considered.

Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for \ion{H}{1} self-shielding against the UV background (see \citep{GrackleMethod} for more details of this implementation). We assume \ion{He}{1} ionization generally follows \ion{H}{1}. This allows us to approximate \ion{He}{1} self-shielding using the same form (A. Rahmati, private communication). We ignore \ion{He}{2} photoionization from the UV background entirely. Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from Cloudy (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \texttt{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

@@

Following the initialization procedure of \citet{Hu2017}, we use artificial supernova driving to generate realistic densities and turbulent properties in the galaxy ISM. This additionally prevents an otherwise uniform collapse of the gas disk. The supernovae explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}. We stop the artificial driving 25~Myr after the first star particle forms. These artificial supernova do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.

@@

We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and O column density projections (fourth row), at four different times in the simulation \textit{(list times here)}. In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points. Towards the end of the simulation time, the half light radius is $389 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.

@@

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{textbf{Draft figure - need to pretty up and finalize fields and times.} Edge-on views of our dwarf galaxy at four different times in its evolution, beginning with the time at first star formation and ending at XXX Myr. Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving \ion{H}{1} column density (third row) and O column density (fourth row). Additionally, each individual main sequence star particle is shown in the number density projections as a single black dot.}
\label{fig:panel_x}
\end{figure*}

@@

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about \textbf{$6 \times 10^5$ M$_{\odot}$, or roughly 17\%} of the total mass in the galaxy's disk. The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases to about \textbf{25\%} as the total amount of mass in the disk decreases through feedback driven winds. Small drops in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy is discussed further in context with other works in Section~\ref{sec:observation}.

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{sfr_snr}
\includegraphics[width=0.475\linewidth]{mass_evolution}
\caption{Left: The SFR and core collapse SNR in our dwarf galaxy in 10 Myr bins (left). Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the galaxy over time. Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and SNR.}
\label{fig:sfr_mass_evolution}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{1D radial profiles of the ISRF in our galaxy in three different bands, time-averaged over the final 50 Myr of simulation time. The top panel gives $G_{\rm o}$, or the flux of radiation between 6 - 13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position. The bottom panel gives the \ion{H}{1} and \ion{He}{1} ionizing stellar radiation flux, showing average value and maximum values only. For these fields the minimum value reaches zero at some point over the examined period at all radii.}
\label{fig:ISRF}
\end{figure}

The bottom panel gives the ionizing photon fluxes (\ion{H}{1} and \ion{He}{1}) from ionizing photons from the stellar radiation \texttt{only}. Since these fields are tracked directly with ray-tracing radiative transfer, the profiles encode information about local attenuation of these photons from dense, neutral gas. This is the main driver of the differences between these fields and $G_{\rm o}$. In addition, we only show the average line and shade to the maximum value at any given position, since the minimum value reaches zero at all radii at some point over the 50 Myr examined. As shown, this causes the profile to vary much more dramatically at all radii. However, the same general trend is preserved of less radiation in the inner 200 pc than the region between 200 and 400 pc, and an order of magnitude or more fluctuation at all radii. The rapid drop off beyond 400 pc is due to the rapid attenuation of ionizing photons by the cold gas at large radii (see Figure~\ref{fig:panel_x}).

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots of the ISRF in two flux bands, $G_{\rm o}$ and \ion{H}{1} ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within 25 pc of the midplane of our dwarf galaxy. We note the large difference in color scale between the two plots. Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to \ion{H}{1} ionizing radiation, it does not show up in the \ion{H}{1} ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ since we assume it to be optically thin, though do apply a localized shielding approximation.}
\label{fig:ISRF_2D}
\end{figure*}

@@

The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted \ion{H}{1} surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, Tollerud2015, Sand2015}. However, the sample of isolated dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small. In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) law (left) for low mass galaxies, and the extended Schmidt law (ESL) (right) which has been shown recently to be extend to low mass, low metallicity dwarf galaxies \citep{Roychowdhury2017}. We plot our galaxy every 1 Myr in these diagrams, showing the significant temporal variation in both spaces. Although these quantities are conceptually simple, due to how these values are measured observationally it is challenging to make a direct comparison to simulations, particularly in defining the geometric region to measure the surface densities. We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs following what is described in \citet{Roychowdhury2014}. We define $\Sigma_{\rm sfr} = \dot{M}_{*, \rm{10 Myr}} / A_{*, \rm{10 Myr}}$, where $\dot{M}_{*, \rm{10 Myr}}$ is the SFR measured over the preceding 10 Myr, and $A_{*, \rm{10 Myr}}$ is the disk defined out to the farthest star formed within the previous 10 Myr. Likewise, $\Sigma_{\rm gas} = M_{\rm gas, 10 Myr} / A_{*, \rm{10 Myr}}$, where M$_{\rm gas, 10 Myr}$ is the total gas mass within this defined disk. However, the total gas content cannot be determined observationally, particularly for low mass dwarf galaxies with a virtually unmeasurable H$_2$ content. Therefore, we present $\Sigma_{\rm gas}$ as measured directly in the simulations (green/purple points) and the observational equivalent, or $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He, and where there is no correction for H$_2$ (plasma points).

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution}
\includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution}
\caption{The KS law (left) and ESL (right) relationships for our galaxy as measured every 1 Myr for the total gas surface density computed from the simulations, and an observational analog derived using the \ion{H}{1} content (see text for details).}
\label{fig:KS}
\end{figure*}

@@

Unfortunately, these high resolution simulations are not (yet) run for the $\sim$ Gyr timescales required to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at z = 0. However, we can compare to a key observable, the ejection / retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from stellar evolution models based on the galaxy's star formation history. This can be done readily with Milky Way dSph's, whose stars seem to retain very little of the expected metals produced, on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}. However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy. Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gaseous, star forming low mass dwarf galaxy close enough to the Milky Way to conduct this experiment and with an observable \ion{H}{2} region, necessary for determining gas phase abundances. Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}. As discussed in Section~\ref{sec:chemical evolution}, roughly \textbf{95\%} of the tracked metals produced throughout the simulation time no longer reside within the galaxy's disk. At the end of our simulation, we agree with the observations; however, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs. Although more than half of these metals are expected to be re-accreted \citep{Angles-Alcazar2017}, it is still possible that, at any moment, most of the metals that have been produced lie outside the galaxy disk. We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.

@@

\section{Stellar Radiation Properties}
\label{appendix:radiation}
We detail the radiation properties of our model stars as a function of stellar mass and metallicity, both of which are assigned directly from an IMF and from the local gas properties respectively. The stellar radiation properties are a determined from the OSTAR2002 grid \citep{Lanz2003} (or as integrated from an adjusted black body curve for stars off of the OSTAR2002 grid) given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set. In Figure~\ref{fig:stellar radiation properties} we plot the ionizing photon luminosities for \ion{H}{1} (top left) and \ion{He}{1} (top right) for each star, the FUV (middle left) and LW (middle right) luminosities, and finally the \ion{H}{1} ionizing radiation photon energy (bottom left) and \ion{He}{1} ionizing photon energy (bottom right). We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass. This requires two factors for each radiation type, one for low mass and one for high mass stars. We use the following multiplicative factors to adjust the black body spectrum for \ion{H}{1} and \ion{He}{1} radiation respectively: [0.1, 3.2] and [0.0001, 4.0]. We do not find this adjustment to be necessary for the FUV and LW radiation bands.
